Relevance-based Quantization of Scattering Features for Unsupervised Mining of Environmental Audio

### 2018-02-15 paper/structureScene.tex
more comments on writing
typo

The metric $p@k$ is computed for $k=\lbrace 1,\ldots,9\rbrace$, since each class only has $10$ items. Note that a $p@1$ is equivalent to the classification accuracy obtained by the classifier which chooses the label of the closest neighbor for a given item. The \emph{RbQ} approaches are compared to commonly used early integration approach \emph{early}, which consists in averaging over time the feature set of each scene, resulting in one feature vector per scene. The parameters of the BOF approach are the one used in \cite{aucouturier2007bag}, \textit{i.e.} 10 Gaussians per scene estimated using the Expectation Maximization (EM) algorithm. Gaussian models are compared using Monte-Carlo sampling approaximation. In order to ensure convergence of the EM algorithm when considering the scattering features as input, the dimension of the feature vector is reduced from 1367 to 30 by projecting the features over the 30 principal components computed over the whole dataset. \vl{Too much passive voice, too many instances of "use", "used".}

@@

For the scattering transform, both \emph{RbQ-c} and \emph{RbQ-w} outperform \emph{early}, thus confirming the benefits of using an relevance-based quantization (\emph{RbQ}) to improve the similarity measures between the scenes. However, it is worth noticing that \emph{RbQ-a} performs worse or comparably to \emph{early}, showing that the discriminant information is destroyed by averaging the contributions from all centroids. This result is in line with the findings of \cite{lagrange:hal-01082501}. To take advantage of such a representation, we need to select certain representative centroids when comparing quantized objects. Furthermore, it appears that \emph{RbQ-c} is better able to characterize the classes compared to \emph{RbQ-w}. This last observation suggests that weighting a centroid according to the number of frames it contains may prove to be a limited solution. Indeed, nothing a priori indicates that the discriminant information between two scenes lays within the majority of their frames. On the contrary, two similar environments may share a lot of similar sound sources with only a few sources discriminating between them. \ml{This is a bit of a stretch, since it may just be that we used the wrong distance to take the weighting into account. Perhaps the non-normalize d EMD is not appropriate here?}

@@

Considering $p@5$ as our metric (as in \cite{aucouturier2007bag} and \cite{lagrange:hal-01082501}), the use of the log-scattering transform instead of MFCCs increases the performance from $0.31$ to $0.49$ and the use of the relevance-based quantization approach using the closest similarity (\emph{RbQ-c}) further improves the performance to $0.54$ for a global increase of $0.23$.

>>>>

The metric $p@k$ is computed for $k=\lbrace 1,\ldots,9\rbrace$, since each class only has $10$ items. Note that a $p@1$ is equivalent to the classification accuracy obtained by the classifier which chooses the label of the closest neighbor for a given item. The \emph{RbQ} approaches are compared to commonly used early integration approach \emph{early}, which consists in averaging over time the feature set of each scene, resulting in one feature vector per scene. The parameters of the BOF approach are the one used in \cite{aucouturier2007bag}, \textit{i.e.} 10 Gaussians per scene estimated using the Expectation Maximization (EM) algorithm. Gaussian models are compared using Monte-Carlo sampling approximation. In order to ensure convergence of the EM algorithm when considering the scattering features as input, the dimension of the feature vector is reduced from 1367 to 30 by projecting the features over the 30 principal components computed over the whole dataset. \vl{Too much passive voice, too many instances of "use", "used".}

@@

For the scattering transform, both \emph{RbQ-c} and \emph{RbQ-w} outperform \emph{early}, thus confirming the benefits of using an relevance-based quantization (\emph{RbQ}) to improve the similarity measures between the scenes. However, it is worth noticing that \emph{RbQ-a} performs worse or comparably to \emph{early}, showing that the discriminant information is destroyed by averaging the contributions from all centroids. This result is in line with the findings of \cite{lagrange:hal-01082501}. To take advantage of such a representation, we need to select certain representative centroids when comparing quantized objects. Furthermore, it appears that \emph{RbQ-c} is better able to characterize the classes compared to \emph{RbQ-w}. This last observation suggests that weighting a centroid according to the number of frames it contains may prove to be a limited solution. Indeed, nothing a priori indicates that the discriminant information between two scenes lays within the majority of their frames. On the contrary, two similar environments may share a lot of similar sound sources with only a few sources discriminating between them. \ml{This is a bit of a stretch, since it may just be that we used the wrong distance to take the weighting into account. Perhaps the non-normalized EMD is not appropriate here?}

@@

Considering $p@5$ as our metric (as in \cite{aucouturier2007bag} and \cite{lagrange:hal-01082501}), the use of the log-scattering transform instead of MFCCs increases the performance from $0.31$ to $0.49$ and the use of the relevance-based quantization approach using the closest similarity (\emph{RbQ-c}) further improves the performance to $0.54$ for a global increase of $0.23$. \vl{Too many instances of ``use'', ``use'', ``using''. It is worth reminding what the baselines are.}
